Fast Sorting on Modern Computers

### 2005-05-26 paper/docs/report.tex
make way for the new and improved fs
an extra file snuck ast me making changes for the updated listings package

\documentclass[dvips]{report}
\usepackage{varioref}
\usepackage{listings}
\usepackage{color}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{float}
\usepackage{lgrind}

@@

\lstset{language=c,tabsize=3,basicstyle=\small,visiblespaces=false,visibletabs=false,stringspaces=false,labelstep=1,labelstyle=\small,frame=tblr}

@@

@@

\chapter*{Acknowledgements}
I would like to thank my supervisor, Dr. David Gregg, for his help and advice
during this project. I'd also like to thank those who read my first draft, and
my friends and family for their support during the last year, and my entire time
at college. Thank you.
\newpage

@@

@@

%\appendix

%\chapter{Simulation Result Listing}
%\input result_list.tex

%\chapter{Code Listing}
%\input code_list.tex

%\chapter{Bug List}
%\input bugs.tex

%\chapter{SimpleScalar installation}
%\input simplescalar.tex

>>>>

\documentclass[dvips]{report}
\usepackage{ifthen}
\usepackage{varioref}
\usepackage{listings}
\usepackage{color}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{float}
\usepackage{lgrind}

@@

\newcommand{\sixplot}[7]{
\afterpage{
\setcounter{subfigure}{0}
\thispagestyle{empty}
\clearpage
\enlargethispage{14em}
\vspace*{-5em}
\begin{figure}[H]
\begin{changemargin}
\subfigure[]{\includegraphics[scale=0.74]{../counters/#1}}
\ifthenelse{\equal{#2}{}}{}{\subfigure[]{\includegraphics[scale=0.74]{../counters/#2}}}
\ifthenelse{\equal{#3}{}}{}{\subfigure[]{\includegraphics[scale=0.74]{../counters/#3}}}
\ifthenelse{\equal{#4}{}}{}{\subfigure[]{\includegraphics[scale=0.74]{../counters/#4}}}
\ifthenelse{\equal{#5}{}}{}{\subfigure[]{\includegraphics[scale=0.74]{../counters/#5}}}
\ifthenelse{\equal{#6}{}}{}{\subfigure[]{\includegraphics[scale=0.74]{../counters/#6}}}
\end{changemargin}
\vspace*{6em}
\caption{Branch prediction performance for #7. All graphs use the same scale.}
\label{Branch prediction performance for #7}
\end{figure}
\newpage
}}

\lstset{language=c,tabsize=3,basicstyle=\small,showspaces=false,showtabs=false,showstringspaces=false,stepnumber=1,numberstyle=\small,frame=tblr}

@@

%TODO make the page wider
%TODO aspell in UK english

@@

\chapter*{Acknowledgments}
I would like to thank my supervisor, Dr. David Gregg, for his help and advice
during this project. I'd also like to thank those who read my first draft, and
my friends and family for their support during the last year, and my entire time
at college. Thank you.
\newpage

@@

\chapter{Shellsort}

\input shell.tex

@@

\appendix

\chapter{Simulation Result Listing}
\input result_list.tex

%\chapter{Software Predictor Result Listing}
%\input software_predictor.tex

\chapter{Code Listing}
\input code_list.tex

% the bugs are now fixed (actually, one of them was only mistakenly a bg :)
% the only remaining thing is the compulsory cache subtraction.
\chapter{Bug List}
\input bugs.tex

\chapter{SimpleScalar installation}
\input simplescalar.tex
